\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{url}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\begin{document}

\title{Consensus-Driven Evaluation of Medical AI Answers:
A Privacy-Preserving Multi-SLM Judge Framework}

\author{
\IEEEauthorblockN{First Author}
\IEEEauthorblockA{\textit{Department Name} \\
\textit{University / Institution}\\
City, Country \\
email@domain}
\and
\IEEEauthorblockN{Second Author}
\IEEEauthorblockA{\textit{Department Name} \\
\textit{University / Institution}\\
City, Country \\
email@domain}
}

\maketitle

% -------------------------------------------------------------------
\begin{abstract}
Automated evaluation of AI-generated medical answers typically relies
on a single large, cloud-hosted model, posing HIPAA compliance risks
and precluding offline deployment. We present Multi-SLMs-as-Judge,
a privacy-preserving framework that assembles a panel of four locally
deployed small language models (SLMs, $\leq$7B parameters) to evaluate
medical answer quality entirely on local hardware. Inter-judge consensus
is quantified via a normalized pairwise agreement score ($\mathrm{Agr}$),
which gates quality score reporting and routes low-consensus cases to
human review rather than silently accepting an unreliable result.
Across 100 clinical questions spanning five domains and five evaluation
rubrics, binary-scale rubrics achieve mean agreement of 91--94\%, while
Likert-scale rubrics fall to 72--81\%. A controlled comparison using
identical rubric criteria at different scales isolates a 22
percentage-point drop attributable solely to scale choice. Cardiology
is the most consistently judged domain; pharmacology generates the most
disagreement, driven primarily by Likert rubrics. These findings offer
practical guidance for rubric design and scoring-scale selection in
privacy-safe clinical evaluation pipelines.
\end{abstract}

\begin{IEEEkeywords}
medical AI evaluation, small language models, inter-judge agreement,
privacy-preserving NLP, rubric design, local deployment, e-health
\end{IEEEkeywords}

% -------------------------------------------------------------------
\section{Introduction}

Reliable evaluation of AI-generated medical answers is a prerequisite
for safe clinical deployment. The dominant approach routes answers to a
single large, closed-source model---such as GPT-4~\cite{achiam2023gpt}---
acting as an automated judge~\cite{zheng2023judging}. In healthcare this
creates two compounding problems. First, routing protected health
information through a third-party API raises significant HIPAA
compliance concerns~\cite{cohen2017hipaa}. Second, dependence on remote
inference makes such systems unavailable in offline or
bandwidth-constrained environments such as mobile point-of-care tools.
Beyond these structural barriers, single-model judges carry well-documented
reliability problems: some favor longer responses regardless of quality
~\cite{wang2023verbosity}, exhibit self-preference bias~\cite{panickssery2024bias},
and produce ratings that shift with superficial prompt rewording~\cite{zeng2023framing}.

Small language models (SLMs) that run entirely on-device offer a promising
alternative. Yet the proliferation of open-source medical SLMs makes it
non-trivial to select a single trustworthy judge. Rather than committing
to one model, we ask whether a \emph{panel} of SLMs---analogous to a
committee of expert reviewers---can collectively produce more reliable
evaluations than any individual judge. Consensus among diverse models
serves as an internal reliability signal, while disagreement flags
cases warranting human review.

We address this gap with \textbf{Multi-SLMs-as-Judge}, a modular framework
that (1)~runs a configurable panel of locally deployed SLMs with no
external API call, (2)~computes a pairwise agreement score to determine
routing, and (3)~reports a quality score only when sufficient consensus
is reached. Our main contributions are:
\begin{itemize}
  \item A consensus-gated evaluation pipeline that transforms panel
        disagreement into an actionable routing signal rather than a
        silent failure.
  \item Three controlled experiments separating the effects of rubric
        design, scoring scale, and clinical domain on inter-judge agreement.
  \item Empirical evidence that scoring scale has a large, independent
        effect on agreement: switching from binary to Likert on identical
        criteria drops agreement by 22 percentage points.
  \item Practical deployment guidance derived from per-domain and
        per-rubric breakdowns, including threshold tuning recommendations.
\end{itemize}

% -------------------------------------------------------------------
\section{Related Work}

\subsection{LLM-as-Judge}
Zheng et al.\ introduced MT-Bench and showed that GPT-4 judgments match
human preferences nearly as well as human-to-human agreement~\cite{zheng2023judging}.
Kim et al.\ built Prometheus, a rubric-trained evaluator that improves
instruction-following consistency~\cite{kim2024prometheus}. Li et al.\
showed that single-model judges benefit substantially from multi-criteria
rubrics~\cite{li2023generative}. Known failure modes include
self-preference bias~\cite{panickssery2024bias} and sensitivity to
prompt framing~\cite{zeng2023framing}. None of these studies tests
scoring scale as a separate variable.

\subsection{Panel and Ensemble Evaluation}
Verga et al.\ demonstrated that a jury of diverse smaller models can
match single large-judge reliability at lower cost~\cite{verga2024replacing}.
Chan et al.\ showed that multi-agent debate among diverse judges
improves evaluation fidelity~\cite{chan2023chateval}. Wu et al.\ found
that ensemble judges reduce position bias in summarization
evaluation~\cite{wu2023ensemble}. These studies establish the value of
panel diversity but do not separate rubric, scale, and domain effects.

\subsection{Medical AI Evaluation}
Singhal et al.\ evaluated PaLM on clinical questions using physician
ratings~\cite{singhal2023large}. Nori et al.\ tested GPT-4 on USMLE-style
problems, finding strong benchmark performance but limited insight into
evaluation reliability~\cite{nori2023gpt4}. HealthBench, developed with
input from 262 physicians, provides physician-written criteria for
clinical answer evaluation~\cite{arora2025healthbench}. Ho et al.\
reviewed qualitative metrics for clinical LLM evaluation~\cite{ho2024qualitative}.
Labrak et al.\ emphasized the need for domain-aware rubrics in medical
NLP~\cite{labrak2024biomistral}. To our knowledge, no prior work has
systematically studied multi-SLM judge panels for medical answer evaluation.

% -------------------------------------------------------------------
\section{Multi-SLMs-as-Judge Framework}

\subsection{System Overview}

Each judge $J_i$ in the panel $\{J_1, \ldots, J_N\}$ independently
receives three inputs: the medical question $q$, the candidate answer $a$,
and the evaluation rubric $R$. The system proceeds in two strictly
ordered steps. First, the pairwise agreement score $\mathrm{Agr}$ is
computed across all judge pairs. Second, if and only if $\mathrm{Agr}$
exceeds a configurable threshold, the quality score $\hat{S}$ is computed
and reported. This ordering is deliberate: reporting a quality score when
judges strongly disagree would give users a false sense of confidence.
By checking agreement first, the framework turns judge disagreement into
an actionable routing signal.

\subsection{Pairwise Agreement Score}

Let $s_i^k$ denote the score assigned by judge $i$ to criterion $k$,
and $\max_k$ the maximum achievable score for that criterion.
The normalized pairwise agreement score is:

\begin{equation}
\mathrm{Agr} = \frac{2}{N(N-1)}\sum_{i < j}
\left(1 - \frac{1}{|R|}\sum_{k=1}^{|R|}
\frac{|s_i^k - s_j^k|}{\max_k}\right)
\label{eq:agr}
\end{equation}

\noindent where $|R|$ is the number of criteria in rubric $R$.
Dividing by $\max_k$ normalizes each criterion difference to $[0,1]$,
making binary and Likert scores directly comparable across rubrics.
Thus $\mathrm{Agr} \in [0,1]$, where 1.0 indicates perfect consensus
and 0.0 indicates maximum disagreement.

Based on $\mathrm{Agr}$, the framework routes each case to one of four
levels, governed by user-configurable thresholds:
\begin{itemize}
  \item \textbf{Full Agreement (FA):} $\mathrm{Agr} \geq \theta_{FA}$
        --- judges are nearly unanimous; $\hat{S}$ is delivered as
        fully reliable.
  \item \textbf{Majority Agreement (MA):} $\theta_{MA} \leq \mathrm{Agr}
        < \theta_{FA}$ --- panel broadly agrees; $\hat{S}$ is delivered
        with a confidence note.
  \item \textbf{Split (SP):} $\theta_{SP} \leq \mathrm{Agr} < \theta_{MA}$
        --- panel is genuinely divided; case routed to human review.
  \item \textbf{Disagreement (D):} $\mathrm{Agr} < \theta_{SP}$
        --- substantial disagreement; case escalated to domain expert.
\end{itemize}

Default thresholds for a four-judge panel: $\theta_{FA}=0.95$,
$\theta_{MA}=0.75$, $\theta_{SP}=0.50$. These correspond to near-unanimous,
supermajority, and coin-flip agreement levels respectively. Operators
should recalibrate thresholds using historical data when panel size
or clinical context changes.

\subsection{Quality Score}

The quality score is reported only when $\mathrm{Agr} \geq \theta_{MA}$.
It is computed as the criterion-weighted mean of all judges' normalized
scores:

\begin{equation}
\hat{S} = \frac{1}{N}\sum_{i=1}^{N}
\frac{\sum_{k=1}^{|R|} w_k \cdot (s_i^k / \max_k)}{\sum_{k=1}^{|R|} w_k}
\label{eq:score}
\end{equation}

\noindent where $w_k$ is the weight of criterion $k$ (default $w_k=1$,
equal weighting). The resulting $\hat{S} \in [0,1]$ summarizes how well
the answer satisfies the rubric's criteria.

When one judge's scores deviate substantially from the rest, the
framework offers three configurable strategies: (A)~include all judges
equally (simpler, no silent exclusion); (B)~remove the most deviant
judge before computing $\hat{S}$ (more robust but reduces transparency);
or (C)~down-weight outlier judges via inverse-variance weighting. When
$\mathrm{Agr} < \theta_{SP}$, no outlier-handling strategy is reliable
because there is no stable majority to serve as a reference---escalation
to human review is the only safe option.

\subsection{Worked Example}

Consider the question: \textit{``What is the first-line treatment for
anaphylaxis?''} The candidate answer states: \textit{``Administer
epinephrine 0.3\,mg IM into the lateral thigh immediately. Place patient
supine. Call emergency services.''} Under the HealthBench rubric, four
judges independently score five binary criteria (correctness, safety,
escalation, uncertainty, referral). Suppose Judges 1, 3, and 4 each
score $[1,1,1,1,1]$ while Judge 2 scores $[1,1,1,0,1]$, judging that
the answer does not sufficiently acknowledge uncertainty. This yields
$\mathrm{Agr} = 0.88$ (Majority Agreement) and $\hat{S} = 0.90$,
delivered with a confidence note flagging the divergence on criterion 4.

% -------------------------------------------------------------------
\section{Evaluation Rubrics and Benchmark}

\subsection{Rubrics}

Five rubrics covering patient communication, clinical safety, and
general quality assessment are evaluated. Table~\ref{tab:rubrics}
summarizes their criteria and default scales.

\begin{table}[htbp]
\caption{Medical Answer Evaluation Rubrics}
\label{tab:rubrics}
\begin{center}
\small
\begin{tabular}{|l|l|p{3.8cm}|}
\hline
\textbf{Rubric} & \textbf{Scale} & \textbf{Criteria} \\
\hline
PEMAT (R1)~\cite{shoemaker2014development} & Binary & Plain language, organized, focused; actionable steps, barriers \\
\hline
HealthBench (R2)~\cite{arora2025healthbench} & Binary & Correctness, safety, escalation, uncertainty, referral \\
\hline
ClinicalEval (R3)~\cite{ho2024qualitative} & Likert 1--5 & Accuracy, safety, relevance, completeness, clarity \\
\hline
Prometheus (R4)~\cite{kim2024prometheus} & Likert 1--5 & Instruction-following, factuality, coherence, completeness \\
\hline
PEMAT-Likert (R5) & Likert 1--5 & Same as PEMAT (scale variant only) \\
\hline
\end{tabular}
\end{center}
\end{table}

PEMAT~\cite{shoemaker2014development} uses binary criteria specifically
designed to assess whether patient education materials are written in
plain language and provide clear, actionable guidance. HealthBench
~\cite{arora2025healthbench} evaluates five safety-critical dimensions
drawn from physician-authored criteria. ClinicalEval~\cite{ho2024qualitative}
measures overall clinical utility on a 1--5 Likert scale. Prometheus
~\cite{kim2024prometheus} targets instruction-following and factual
grounding. PEMAT-Likert (R5) is identical to PEMAT in criteria but
replaces the binary scale with a 1--5 Likert scale, forming a controlled
pair that directly isolates the effect of scale width from rubric content.

\subsection{Benchmark Dataset}

The evaluation benchmark contains 100 questions drawn from three
publicly available, human-evaluated medical QA collections:
MedQuAD~\cite{ben-abacha-medquad-2019}, MedDialog~\cite{chen-meddialog-2020},
and Medical Meadow~\cite{singhal-medical-meadow-2023}. Twenty questions
were sampled from each of five clinical domains: cardiology, pharmacology,
neurology, pediatrics, and emergency medicine. All answers were written
or verified by medical professionals, meaning the benchmark contains
realistic quality variation---including ambiguous, partially correct,
and occasionally wrong responses---that puts real pressure on the judges
in a way that clean synthetic data cannot.

Domains were chosen to represent a range of clinical guideline maturity.
Cardiology has highly standardized protocols (STEMI, atrial fibrillation,
heart failure). Pharmacology requires precise numerical knowledge---drug
interactions, dosing thresholds, contraindications---that small models
may encode inconsistently. Neurology, pediatrics, and emergency medicine
fall in between, involving clear guidelines alongside room for clinical
interpretation.

\subsection{Judge Panel}

The panel consists of four locally deployable SLMs spanning three
distinct base architectures, as listed in Table~\ref{tab:judges}.
Architectural diversity is intentional: it reduces the risk that all
four models share the same systematic bias or knowledge gap.

\begin{table}[htbp]
\caption{Four-Judge Panel. All models run locally via vLLM with greedy
decoding (temperature~$=0.0$, max 1024 tokens). No external API is used.}
\label{tab:judges}
\begin{center}
\small
\begin{tabular}{|l|l|c|}
\hline
\textbf{Model} & \textbf{Base Architecture} & \textbf{Params} \\
\hline
MedGemma-4B-IT~\cite{sellergren2025medgemma}  & Gemma-3       & 4B \\
BioMistral-7B-DARE~\cite{labrak2024biomistral} & Mistral-DARE  & 7B \\
Meditron-7B~\cite{chen2023meditron70b}         & LLaMA-2       & 7B \\
MedAlpaca-7B~\cite{han2023medalpaca}           & LLaMA-2       & 7B \\
\hline
\end{tabular}
\end{center}
\end{table}

All models were served on a local high-performance server (64-core CPU,
128~GB RAM) with no data transmitted to any external service, satisfying
HIPAA data-governance requirements~\cite{cohen2017hipaa}.

% -------------------------------------------------------------------
\section{Results}

We run three experiments, each holding two variables constant while
varying the third. \textbf{Exp1} varies the rubric at its default
scale. \textbf{Exp2} varies the scoring scale with rubric content
held fixed. \textbf{Exp3} varies the clinical domain aggregated over
all rubrics.

\subsection{Exp1: Rubric Comparison at Default Scale}

Table~\ref{tab:exp1} reports mean pairwise agreement ($\mathrm{Agr}$),
quality score ($\hat{S}$), and the distribution of routing outcomes
for all five rubrics at their default scales.

\begin{table}[htbp]
\caption{Exp1 --- Rubric comparison at default scale ($N$=100, 4-judge panel).
Agr = mean pairwise agreement $\pm$ std. FA/MA/SP/D = count of cases
per routing class out of 100.}
\label{tab:exp1}
\begin{center}
\small
\begin{tabular}{|l|l|r|r|r|r|r|r|}
\hline
\textbf{Rubric} & \textbf{Scale} & \textbf{Agr\%} & \textbf{$\hat{S}$} & \textbf{FA} & \textbf{MA} & \textbf{SP} & \textbf{D} \\
\hline
PEMAT (R1)        & Binary & $94.1{\pm}10.5$ & $.68{\pm}.12$ & 72 & 24 &  4 & 0 \\
HealthBench (R2)  & Binary & $91.3{\pm}9.9$  & $.75{\pm}.10$ & 51 & 38 & 10 & 1 \\
ClinicalEval (R3) & Likert & $80.9{\pm}13.3$ & $.72{\pm}.14$ &  6 & 61 & 30 & 3 \\
Prometheus (R4)   & Likert & $74.0{\pm}16.2$ & $.55{\pm}.18$ & 17 & 53 & 29 & 1 \\
PEMAT-Likert (R5) & Likert & $72.2{\pm}8.9$  & $.60{\pm}.11$ &  5 & 50 & 44 & 1 \\
\hline
\end{tabular}
\end{center}
\end{table}

The two binary rubrics (PEMAT, HealthBench) consistently outperform
the three Likert rubrics. PEMAT reaches 94.1\% agreement and a
full-agreement rate of 72 out of 100 questions. Its criteria---plain
language, organized structure, focused content, actionable steps, and
barriers to action---have clear yes/no thresholds that all four models
recognize similarly, leaving little room for disagreement.

HealthBench scores slightly lower at 91.3\% because two of its five
criteria---HB4 (acknowledges uncertainty) and HB5 (recommends
referral)---require models to judge implicit clinical intent rather than
observable surface features. Deciding whether an answer sufficiently
acknowledges uncertainty is harder to agree on with a binary vote than
deciding whether it uses plain language.

Among Likert rubrics, ClinicalEval (80.9\%) outperforms Prometheus
(74.0\%) because its criteria (accuracy, safety, relevance, completeness,
clarity) have more concrete anchors. Prometheus's criteria---especially
coherence and instruction-following---are more subjective, leading to
high standard deviation (16.2\%) and wide swings in per-question agreement.

The PEMAT controlled pair delivers the clearest single result: PEMAT
binary (R1, 94.1\%) versus PEMAT-Likert (R5, 72.2\%) use \emph{exactly
the same five criteria}. The 22 percentage-point drop is attributable
entirely to switching the scale from binary to Likert 1--5.

\textbf{On quality scores ($\hat{S}$).} Mean scores range from 0.55
to 0.75, lower than those typically reported by large cloud judges
(0.85--0.95). This is expected for three reasons: small local models
tend to be conservative scorers; the benchmark contains difficult,
ambiguous human-authored answers rather than polished AI outputs; and
rubrics include strict safety criteria that most short answers partially
fail. A $\hat{S} = 0.68$ under PEMAT binary means the panel judged
approximately 68\% of rubric criteria were met---for a challenging
benchmark, this is an informative and appropriate signal.

\subsection{Exp2: Scoring Scale Sensitivity}

Table~\ref{tab:exp2} reports mean pairwise agreement for all five
rubrics re-scored under three controlled scales: binary $\{0,1\}$,
Likert 1--5, and 0--10. All criteria and weights were held constant;
only the scale changed.

\begin{table}[htbp]
\caption{Exp2 --- Mean pairwise agreement (\%) by scoring scale.
Bold = highest Agr per rubric. Std in parentheses.}
\label{tab:exp2}
\begin{center}
\small
\begin{tabular}{|l|r|r|r|}
\hline
\textbf{Rubric} & \textbf{Binary} & \textbf{Likert 1--5} & \textbf{0--10} \\
\hline
PEMAT (R1)        & $\mathbf{94.1}_{(10.5)}$ & $71.5_{(10.6)}$ & $88.6_{(4.1)}$ \\
HealthBench (R2)  & $91.3_{(9.9)}$ & $80.8_{(14.5)}$ & $\mathbf{92.6}_{(5.7)}$ \\
ClinicalEval (R3) & $\mathbf{96.8}_{(9.6)}$ & $80.9_{(13.3)}$ & $92.1_{(5.5)}$ \\
Prometheus (R4)   & $91.3_{(17.7)}$ & $74.0_{(16.2)}$ & $\mathbf{89.4}_{(6.4)}$ \\
PEMAT-Likert (R5) & $\mathbf{94.1}_{(10.6)}$ & $72.2_{(8.9)}$ & $88.5_{(4.2)}$ \\
\hline
\end{tabular}
\end{center}
\end{table}

Binary scoring is not universally superior. For rubrics with natural
yes/no thresholds (R1, R3, R5), binary achieves the highest agreement.
ClinicalEval binary (96.8\%) is the single highest value observed across
all experiments---its five criteria each have clear binary thresholds
that the panel recognizes consistently.

For HealthBench and Prometheus, the 0--10 scale achieves marginally
higher peak agreement (92.6\% and 89.4\% respectively). Subjective
criteria such as ``acknowledges uncertainty'' or ``coherent'' benefit
from a finer scale that lets judges express small distinctions as
nearby numbers (e.g., 7 vs.\ 8) rather than being forced into different
Likert steps (e.g., 3 vs.\ 4).

The most practically important finding from Exp2 concerns standard
deviation. The 0--10 scale consistently reduces cross-question
variability to 4--7\% across all rubrics. A system that reliably
produces 88\% agreement on every question is often more operationally
trusthworthy than one averaging 94\% with 10.5\% standard deviation,
because the latter routes individual questions to human review
unpredictably. The 0--10 scale is therefore preferable when consistent
routing stability matters more than peak agreement.

\subsection{Exp3: Agreement Across Clinical Domains}

Table~\ref{tab:exp3} reports routing class counts per domain, aggregated
over all five rubrics (5 rubrics $\times$ 20 questions = 100 cases per domain).

\begin{table}[htbp]
\caption{Exp3 --- Panel agreement class counts by domain (100 cases per
domain, default scales). FA=Full Agree, MA=Majority, SP=Split, D=Disagree.}
\label{tab:exp3}
\begin{center}
\small
\begin{tabular}{|l|r|r|r|r|}
\hline
\textbf{Domain} & \textbf{FA} & \textbf{MA} & \textbf{SP} & \textbf{D} \\
\hline
Cardiology   & 36 & 50 & 14 & 0 \\
Neurology    & 31 & 47 & 22 & 0 \\
Pediatrics   & 31 & 46 & 23 & 0 \\
Emergency    & 33 & 41 & 25 & 1 \\
Pharmacology & 20 & 42 & 33 & 5 \\
\hline
\end{tabular}
\end{center}
\end{table}

\textbf{Cardiology} is the most consistently judged domain (36 FA,
0 D). Cardiology guidelines---STEMI protocols, atrial fibrillation
management, heart failure treatment---are among the most standardized
in medicine, and the panel converges reliably on well-documented
correct answers.

\textbf{Pharmacology} is the hardest domain (20 FA, 5 D, 38 combined
SP+D). Drug interactions, dosing thresholds, and contraindication
reasoning require precise numerical knowledge that small 4--7B models
encode inconsistently. Crucially, this contention is not uniform across
rubrics: PEMAT (R1) and HealthBench (R2) show only 2--3 SP+D cases
even in pharmacology, while ClinicalEval (R3) contributes 13 and
PEMAT-Likert (R5) contributes 14 SP+D cases in this domain. This
demonstrates that rubric choice strongly moderates how much domain
difficulty translates into panel disagreement. Teams working in
pharmacology should prefer binary rubrics and raise $\theta_{FA}$
to 0.98 and $\theta_{MA}$ to 0.85.

\textbf{Emergency medicine} shows a notable split rate (25 SP, 1 D).
The single full-disagree case occurs under HealthBench on its escalation
criterion (HB3), confirming that the disagreement traces to a genuine
clinical judgment question---when exactly to escalate a borderline
presentation---rather than a model calibration issue.

\textbf{Neurology and Pediatrics} show moderate contention (22--23 SP,
0 D), reflecting topics that have clear guidelines but also allow some
room for clinical interpretation.

% -------------------------------------------------------------------
\section{Discussion}

\subsection{Interpreting Agreement and Quality Scores}

High inter-judge agreement is a necessary but not sufficient condition
for clinical correctness. Judges may unanimously assign an incorrect
score when an answer's flaw is too subtle for all panel members to
detect. Before any clinical deployment, panel scores should be validated
against physician ratings on a held-out set. We recommend reporting the
correlation with physician scores and a breakdown of Split and
Disagreement cases to quantify residual clinical risk.

The relatively low quality scores in our experiments (0.55--0.75
compared to 0.85--0.95 for large cloud judges) should not be interpreted
as a framework failure. They reflect the combined effect of three design
choices: conservative local models, a challenging benchmark with
ambiguous human-authored answers, and rubrics with strict safety
criteria. $\hat{S}$ is designed to be informative within this evaluation
context, not to be compared cross-system without accounting for these factors.

\subsection{Threshold Tuning and Panel Composition}

The default thresholds ($\theta_{FA}=0.95$, $\theta_{MA}=0.75$,
$\theta_{SP}=0.50$) were calibrated for a four-judge panel. Operators
changing panel size must recalibrate, because the same numeric Agr
value carries different statistical meaning with more or fewer judges.
The per-domain split rates in Table~\ref{tab:exp3} provide a practical
empirical prior for this tuning: pharmacology deployments benefit from
stricter thresholds, while cardiology deployments can accept more
permissive ones.

Before finalizing any panel, we recommend two steps: (1)~run a
rubric-scoring probe on a small held-out set to verify that all
candidate judges produce parseable output across all rubrics; and
(2)~conduct per-judge ablation experiments that report how agreement
changes with and without each model. These checks make panel reliability
visible before it matters in deployment.

\subsection{Practical Deployment Recommendations}

The following recommendations follow directly from our empirical findings:

\begin{itemize}
  \item \textbf{Match scale to rubric.} Use binary scales for rubrics
        with natural yes/no criteria (e.g., PEMAT, HealthBench). Use
        0--10 when consistent routing stability across questions matters
        more than peak agreement.
  \item \textbf{Always route Split and Disagreement to human review.}
        No automated outlier-handling strategy is reliable when the
        panel lacks a stable majority. Automating over SP and D outcomes
        silently amplifies evaluation error.
  \item \textbf{Raise thresholds in high-stakes domains.} Pharmacology
        and emergency medicine warrant $\theta_{FA}=0.98$,
        $\theta_{MA}=0.85$ based on their observed split rates.
  \item \textbf{Validate against physician ratings.} All SP+D cases
        should be reviewed against clinical ground truth before
        reporting framework performance in any real deployment.
\end{itemize}

\subsection{Limitations}

The benchmark contains 100 questions across five domains---sufficient
for directional findings but not for definitive statistical inference.
Rare specialties such as oncology and psychiatry remain untested. All
judges operate under context windows limited to 400 tokens, which
restricts the length of answers that can be reliably evaluated. The
framework does not implement a mediator loop: disagreements are routed
to human reviewers but no automated reconciliation is attempted. Future
work should investigate whether a mediator model can reduce human review
load without introducing new failure modes.

% -------------------------------------------------------------------
\section{Conclusion}

We presented Multi-SLMs-as-Judge, a privacy-preserving framework for
medical answer evaluation using a panel of locally deployed SLMs. The
framework's two-step design---checking inter-judge agreement before
reporting a quality score---transforms panel disagreement from a silent
failure into an actionable routing signal. Three controlled experiments
yield four concrete findings.

First, binary scoring works best for rubrics with natural yes/no
thresholds, reaching 91--97\% mean agreement and the highest
full-agreement rates. Second, the 0--10 scale consistently reduces
cross-question score variation to 4--7\% standard deviation, making
it the better choice when routing stability matters more than peak
agreement. Third, cardiology is the most stable domain; pharmacology
generates the most disagreement, but this is driven by Likert
rubrics---binary rubrics stay below 3 SP+D cases even in pharmacology.
Fourth, scoring scale and domain difficulty can be disentangled, which
means gate thresholds can be tuned independently of rubric design.

Because the framework runs entirely on local hardware and requires no
external API, it is directly applicable to HIPAA-constrained clinical
settings where cloud-based evaluation is not an option. We hope the
controlled experimental design and open release of code, rubrics, and
benchmark data help other teams build and calibrate their own
privacy-safe evaluation pipelines.

% -------------------------------------------------------------------
\section*{Acknowledgment}

The authors thank the developers of MedGemma, BioMistral, Meditron,
and MedAlpaca for making their models publicly available under open
licenses. All benchmark datasets are used under their respective
open licenses.

% -------------------------------------------------------------------
\begin{thebibliography}{00}

\bibitem{achiam2023gpt}
J. Achiam et al., ``GPT-4 technical report,'' \textit{arXiv}
arXiv:2303.08774, 2023.

\bibitem{arora2025healthbench}
R. K. Arora et al., ``HealthBench: Evaluating large language models
towards improved human health,'' \textit{arXiv} arXiv:2505.08775, 2025.

\bibitem{ben-abacha-medquad-2019}
A. Ben Abacha and D. Demner-Fushman, ``A question-entailment approach
to question answering,'' in \textit{Proc. 18th BioNLP Workshop}, 2019.

\bibitem{chan2023chateval}
C.-M. Chan et al., ``ChatEval: Towards better LLM-based evaluators
through multi-agent debate,'' \textit{arXiv} arXiv:2308.07201, 2023.

\bibitem{chen2023meditron70b}
Z. Chen et al., ``MEDITRON-70B: Scaling medical pretraining for large
language models,'' \textit{arXiv} arXiv:2311.16079, 2023.

\bibitem{chen-meddialog-2020}
S. Chen et al., ``MedDialog: Large-scale medical dialogue datasets,''
\textit{arXiv} arXiv:2004.03329, 2020.

\bibitem{cohen2017hipaa}
I. G. Cohen and M. M. Mello, ``Unauthorized disclosure of protected
health information: Criminal and civil HIPAA enforcement actions,''
\textit{JAMA}, vol. 318, no. 14, pp. 1339--1340, 2017.

\bibitem{han2023medalpaca}
T. Han et al., ``MedAlpaca: An open-source collection of medical
conversational AI models and training data,'' \textit{arXiv}
arXiv:2304.08247, 2023.

\bibitem{ho2024qualitative}
C. N. Ho et al., ``Qualitative metrics from the biomedical literature
for evaluating large language models in clinical decision-making:
A narrative review,'' \textit{BMC Med. Inform. Decis. Mak.},
vol. 24, no. 1, p. 357, 2024.

\bibitem{kim2024prometheus}
S. Kim et al., ``Prometheus: Inducing fine-grained evaluation capability
in language models,'' in \textit{Proc. ICLR}, 2024.

\bibitem{labrak2024biomistral}
Y. Labrak et al., ``BioMistral: A collection of open-source pretrained
large language models for medical domains,'' \textit{arXiv}
arXiv:2402.10373, 2024.

\bibitem{li2023generative}
J. Li et al., ``Generative judge for evaluating alignment,''
\textit{arXiv} arXiv:2310.05470, 2023.

\bibitem{nori2023gpt4}
H. Nori et al., ``Capabilities of GPT-4 on medical challenge problems,''
\textit{arXiv} arXiv:2303.13375, 2023.

\bibitem{panickssery2024bias}
A. Panickssery, S. R. Bowman, and S. Feng, ``LLM evaluators recognize
and favor their own generations,'' in \textit{Proc. NeurIPS},
vol. 37, 2024.

\bibitem{sellergren2025medgemma}
A. Sellergren et al., ``MedGemma technical report,'' \textit{arXiv}
arXiv:2507.05201, 2025.

\bibitem{shoemaker2014development}
S. J. Shoemaker, M. S. Wolf, and C. Brach, ``Development of the Patient
Education Materials Assessment Tool (PEMAT),'' \textit{Patient Educ.
Couns.}, vol. 96, no. 3, pp. 395--403, 2014.

\bibitem{singhal2023large}
K. Singhal et al., ``Large language models encode clinical knowledge,''
\textit{Nature}, vol. 620, pp. 172--180, 2023.

\bibitem{singhal-medical-meadow-2023}
K. Singhal et al., ``Towards expert-level medical question answering
with large language models,'' \textit{arXiv} arXiv:2305.09617, 2023.

\bibitem{verga2024replacing}
P. Verga et al., ``Replacing judges with juries: Evaluating LLM
generations with a panel of diverse models,'' \textit{arXiv}
arXiv:2404.18796, 2024.

\bibitem{wang2023verbosity}
P. Wang et al., ``Large language models are not robust multiple choice
selectors,'' \textit{arXiv} arXiv:2309.03882, 2023.

\bibitem{wu2023ensemble}
N. Wu et al., ``Large language models are diverse role-players
for summarization evaluation,'' \textit{arXiv} arXiv:2303.15078, 2023.

\bibitem{zeng2023framing}
Z. Zeng et al., ``Evaluating large language models at evaluating
instruction following,'' \textit{arXiv} arXiv:2310.07641, 2023.

\bibitem{zheng2023judging}
L. Zheng et al., ``Judging LLM-as-a-judge with MT-Bench and chatbot
arena,'' in \textit{Proc. NeurIPS}, vol. 36, 2023.

\end{thebibliography}

\end{document}
